Results

### 2023-03-30 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
adapted participants

Data collection took place between `r format(as.Date(acqui_time[1]), "%Y-%m")` and `r format(as.Date(acqui_time[2]), "%Y-%m")`.
A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session [@ZernaScheffel2022] and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M=`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }SD = `r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$).
Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).

>>>>

Data collection took place between 16th of August 2022 and the 3rd of February 2023.
A total of $N=`r sum(data_survey[,"lay_beliefs_complete"] == 2)`$ participants completed the online survey and were invited to participate in the two lab sessions.
Of these, $N=`r sum(data_survey[,"files_coged_complete"] == 2)`$ participated in the first laboratory session [@ZernaScheffel2022] and $N=`r sum(data_survey[,"followup_ered_complete"] == 2)`$ completed the second laboratory session.
Of these, $n=1$ person had to be excluded from analyses because they did not follow the instructions.
The final sample consisted of $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants (`r length(which(data_descr[which(data_descr[,"ID"] != dplyr::lag(data_descr[,"ID"])),"gender"] == 2))` female; age: $M\text{ }\pm\text{ }SD =`r papaja::printnum(mean(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`\text{ }\pm\text{ }`r papaja::printnum(sd(data_descr[,"age"], na.rm = TRUE), digits = 1, gt1 = TRUE)`$ years old), which is `r format(round((sum(data_survey[,"followup_ered_complete"] == 2)-1)/85, digits = 1), nsmall = 1)` times more than what the highest sample size calculation required.
Please note that sample size for individual calculations may be smaller due to failure of EMG recording ($n=1$) and failure to record utility ratings ($n=`r sum(is.na(data_ER[,"utility"][data_ER[,"block"] == "3_distraction"]))`$).
